Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-15 paper/paper.tex
pass on prio and clustering

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity to find bugs in JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques.

\begin{itemize}

\item \emph{Test transplantation} leverages diversity of test cases to
  find bugs. It evaluates the effects that running test files from a
  given engine have in detecting bugs in other engines. The intuition
  is that developers design test cases with different objectives in
  mind. As such, replaying these tests in different engines could
  reveal unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that similar inputs to those already tested may reveal
problems.
\end{itemize}

@@

\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In constrast
to prior work on test set diversity, this paper explores diversity of
sources of test cases and diversity of implementations with the goal
of finding bugs. Section~\ref{sec:related-work} elaborates related
work on this topic. Differential Testing~\cite{Brumley-etal-ss07} (DT)
has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated---as only one engine is used, the outcomes
of the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of these techniques aforementioned in finding
bugs on \javascript\ engines.

@@

\emph{Results.}~We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's \jsc{}
and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
none in Mozilla's \smonkey{}. Overall, results indicate that both
techniques were successful at finding bugs. Considering cost per bug
found, test transplantation demanded less effort--from the developers
who inspected the alarms---compared to differential testing.

@@

For different reasons, the specification and implementation of
JavaScript are incomplete. Certain parts of the specification are
undefined; it is responsibility of engineers to decide how to
implement these functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\mcodeid{for-in} loop does not clearly specify the iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for optimization~\cite{for-in-undefined}.
As another example, the specification states that if the
\mcodeid{Number.toPrecision()} function is called with multiple
arguments then the floating-point approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Such gap also exists at the
implementation level. Given the speed the specification changes and
the complexity of the language some features are not fully implemented
as can be observed by the Kangax compatibility table~\cite{kangax}.
It is also worth noting that, as in other languages, some elements in
JS have non-deterministic behavior (\eg{}, \mcodeid{Math.random} and
\mcodeid{Date}). A test that make decisions based on these elements
could, in principle, produce different outcomes on different
runs. Carefully-written test cases should not manifest this kind of
flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}.  As
mentioned previously, all those aspects make testing \js\ engines more
challenging.

@@

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected 
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. Table~\ref{tab:engines} lists the engines we
analyzed. It is worth noting that we used GoogleChromeLab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\section{Seed JS files}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines, and 4) test files mined from issue trackers of
these engines.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests we per
engine. Column ``full'' shows the number of test cases associated
with each engine. Column ``pass-in-par.''  shows the number of
test cases that pass in their parent engine. We discarded tests that
fail in their parent engine as we could not reliably indicate the
reason for the failure, so we assumed the test could be broken. We
removed 63 test cases that fail for that reason--6 tests from \jsc{}
and 57 tests from \smonkey. Column ``type-in-all'' shows the number
of test cases whose executions do not throw dynamic type errors in any
of the engines because of an undefined variable or property. We
capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantation, \ie{}, all
tests under the ``type-in-all'' column\Mar{change name to
  type-in-all} but the Test262 tests. We did not consider tests from
the conformance suite as they are more likely to indicate missing
features as opposed to bugs. In addition, engine developers have
access to these test and are encouraged to run them.  Column
``no-fail-in-all'' shows the tests for which all engines pass. This
test set is used in the evaluation of differential testing. Note that
it is a proper subset of the ``type-in-all'' test set. The tests
from this group are used as fuzzing seeds. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure.

\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,2ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};%
    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

%% \Comment{ Column ``full'' shows the number of the test cases found
%%     for that engine, column ``compile-in-all'' shows the number of
%%     test cases for which engines do not throw compile error (\eg{},
%%     undefined name), and column ``no-fail-all'' shows the number of
%%     test cases that pass in all four engines we analyzed.\Mar{explain
%%       ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}}

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test cases per suite.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

\sloppy{}We observed that issue trackers are an important source of
test data and should not be ignored. Analyzing a sample of issues, we
observed that developers either 1) add test cases as attachments of
issues or 2) embed test cases within the textual description of an
issue. The test cases in attachments are longer compared to the test
cases embedded in issue descriptions whereas the latter are more
common. Consequently, we thought we should handle both
cases. Accessing attachments is simpler compared to embedded
tests. For attachments, we wrote a crawler to visit the issue trackers
of all four engines listed in Table~\ref{tab:engines} and were able to
retrieve a total of 627 files
(\jsc{}=147,\veight{}=370 and
\smonkey{}=110). To mine tests from the textual descriptions, we
broke the text describing the issue in paragraphs and used a binary
classifier to label each paragraph as ``code'' or ``not code''. Then,
based on that information, we merged consecutive paragraphs labeled as
``code'' and used a \js\ parser to check well-formedness of the
corresponding code fragment. Using that method we were able to
retrieve a total of \Fix{XX} files
(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}). All those
files were included in Table~\ref{tab:test-suites}.

Surprisingly, we did not find a public classifier to solve the problem
above. For space, we summarize the solution that worked the best in
the following. We used a standard Embeddings NLP
technique~\Fix{cite}\Mar{needs to explain what this ``Embeddings''
  thing does at a high-level. Also, if this stuff exists why we did
  not find a solution off-the-shelf?} that uses a neural
net~\Fix{cite} to keep a dictionary of words and the similarity
distance among them\Mar{but we are talking about sentences. how does
  it go from words to sentences? Note that many words from the
  ``code'' vocabulary are from English!}. In more detail, the
classification model uses a Convolutional Neural Network~\Fix{cite}
classifier with two layers\Mar{why two? is there a meaning for each
  layer?} and has been trained and evaluated using a dataset with 25K
samples of English paragraphs and 25K snippets of \js{}. We ran a
standard \Fix{X}-repeated 10-fold cross validation to evaluate the
model and obtained a predicted accuracy of \Fix{98\%}. This classifier
is publicly available from our website as a separate component.

@@

Figure~\ref{fig:workflow} illustrates the 
differential testing infrastructure used in part of this study. It takes on
input a list of JS files and generates warnings on output. Boxes in
the figure denote encapsulation, arrowed lines denote data flow, and
the cycle icons denote repetition--the leftmost icon indicates that
each file in the input list will be analyzed in separate whereas the
rightmost icon shows that a single file will be fuzzed multiple times.
The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure ignores the input. Otherwise, it considers the input as
potentially fault-revealing; hence, interesting for human
inspection. The infrastructure uses the
open-source tool eshost-cli~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

It is worth noting that a number of reasons exist, other than a bug,
to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
and ~\ref{tab:false-positives}) and there is no clear automatic
approach to precisely distinguish false and true positives. As such, a
human needs to inspect the warning to classify the issue. To
facilitate inspection, we prioritized warnings and clustered them in
groups. We describe these strategies in the following.

@@

We classified warnings in two types, reflecting their likelihood of
manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
with the cases where the test code executed to completion without
violating any internal checks, but it violated assertions declared in
the test itself or its harness. The rationale is that the input is
more likely to be valid as it it did not raise exceptions during the
execution of the application code, but, it manifested discrepancy
through the violation of an assertion declared in the test. In
contrast, warnings of type ``\lo{}'' are more likely to be associated
with invalid inputs. They reflect the cases where the anomaly is
observed during the execution of functions, which are part of the
application. We found that different engines often check
pre-conditions of those functions differently. It can happen, for
example, that one engine enforces a weaker pre-condition on a function
input compared to another engine and that is acceptable.\Comment{ For
  instance, it is acceptable to pass values greater than \Fix{x} to
  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
cases, the infrastructure would observe a discrepancy that is more
likely to be associated with an invalid input produced by the fuzzer,
\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
bug in the engine code. However, as expected, our heuristic is not
precise---``\lo'' warnings can reveal
bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
this example, the test instantiates an \CodeIn{ArrayBuffer} object and
stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception. This
is a case of undocumented precondition, which is handled as a bug. It
was fixed by \chakra\ developers and is no longer present in the most
recent release of \chakra. Despite that case, most bugs we found
emerged from ``\hi{}'' warnings.

%% \Igor{
%%   Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
%%   casos reportados como LO tambem podem ser considerados como um true positive.
%%   Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
%%   se um teste falha antes da linha em que ha uma assercao, entao a falha
%%   ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
%%   possivel observar um caso de bug obtido em um bucket classificado como LO.
%%   Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
%%   posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
%%   maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
%%   de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
%%   lancar Offset is outside the bounds.

%%   Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
%%   Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
%%   correto seria usar um levantar um erro
%% }

@@

Clusterization helps to group tests that fail for similar reasons. We
only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
that arise from the test case, which are typically
distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
error messages produced by a ``\lo'' warning. Any warning, including
this one, that has this same message signature will be included in the
same ``bucket''. To maximize the hit ratio we remove references to
code that may appear in the error messages.

@@

\Fix{...reviewer asks for more details...check what we added in the
  rebuttal for this.}

@@

%% In the following, we describe the list of fuzzers we analyzed. We
%% initially considered generational grammar-based fuzzers and mutational
%% fuzzers.

>>>>

%% WHAT WE DID
This paper reports on a study to evaluate the importance of diversity
to find bugs in JavaScript engines; it covers two complementary
diversity-aware testing techniques.

\vspace{-1ex}
\begin{itemize}
  \setlength\itemsep{0em}
\item \emph{Test transplantation} leverages diversity of test
  cases. It evaluates the effects that running test files from a given
  engine have in detecting bugs in other engines. The intuition is
  that developers design test cases with different objectives in
  mind. As such, replaying these tests in different engines could
  reveal unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of
  engine implementations. More precisely, it fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines using a differential oracle. The
  intuition is that similar inputs to those already tested may reveal
  problems.
\end{itemize}
\vspace{-1ex}

@@

\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In constrast
to prior work on test set diversity, this paper explores diversity of
sources of test cases and diversity of implementations with the goal
of finding bugs. Section~\ref{sec:related-work} elaborates related
work on this topic. Differential Testing~\cite{Brumley-etal-ss07} (DT)
has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach is that
it can be fully automated---as only one engine is used, the outcomes
of the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of these techniques aforementioned in finding
bugs on \javascript\ engines.

@@

\emph{Results.}~We considered engines from four major players--Apple,
Google, Microsoft, and Mozilla. Our results indicate that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
indicate that most of these bugs affected two engines--Apple's \jsc{}
and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
none in Mozilla's \smonkey{}. Overall, results indicate that both
techniques were successful at finding bugs. Considering cost per bug
found, test transplantation demanded less effort from the developers
who inspected the alarms, compared to differential testing.

@@

The specification of JavaScript is incomplete for different
reasons. Certain parts of the specification are undefined; it is
responsibility of engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\js\ \mcodeid{for-in} loop construct does not clearly specify the
iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for loop
optimizations~\cite{for-in-undefined}.  As another example, the
specification states that if the \mcodeid{Number.toPrecision()}
function is called with multiple arguments then the floating-point
approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Given the speed the
specification changes and the complexity of the language some features
are not fully implemented as can be observed by the Kangax
compatibility table~\cite{kangax}.  It is also worth noting that, as
in other languages, some elements in JS have non-deterministic
behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
that make decisions based on these elements could, in principle,
produce different outcomes on different runs. Carefully-written test
cases should not manifest this kind of flaky behavior.  As mentioned
previously, all those aspects make testing \js\ engines more
challenging.

@@

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected 
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. Table~\ref{tab:engines} lists the engines we
analyzed. It is worth noting that we used Google Chrome Lab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\section{JS Files Mined}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines, and 4) test files mined from issue trackers of
these engines.

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed 63
test cases that fail for that reason--6 tests from \jsc{} and 57 tests
from \smonkey. Column ``type-in-all'' shows the number of test cases
whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property. These cases were
captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. For the evaluation of test transplantation, we used
the \totalTestFilesForTestTransplantation{} tests included in the
dashed rectangle under column ``type-in-all'', \ie{}, all tests under
that column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these test and are encouraged to run them. Finally, column
``no-fail-in-all'' shows the tests for which all engines pass. Note
that the set of tests in this column is a subset of the
``type-in-all'' test set. This test set is used in the evaluation of
differential testing as fuzzing seeds. The guarantee that they pass in
all engines assures that, if discrepancies occur, they are related to
the changes in the input as opposed to the original cause of failure.

\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,2ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};%
    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
    shows the tests used for test transplantation (resp., cross-engine
    differential testing).}  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & \marktopleft{c2}17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\markbottomright{c2}\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

\sloppy{}We observed that issue trackers are an important source of
test data and should not be ignored. Analyzing a sample of issues, we
observed that developers either 1) add test cases as attachments of
issues or 2) embed test cases within the textual description of an
issue. The test cases in attachments are longer compared to the test
cases embedded in issue descriptions whereas the latter are more
common. Consequently, we thought we should handle both
cases.

Accessing attachments was engineering-wise simpler compared to
embedded tests. For that, we wrote a crawler to visit the issue
trackers of all four engines listed in Table~\ref{tab:engines} and we
were able to retrieve a total of 627 files (\jsc{}=147, \veight{}=370,
and \smonkey{}=110).

To mine tests from the textual descriptions we proceeded as
follows. First, we broke the text describing the issue in paragraphs
and used a binary classifier to label each paragraph as ``code'' or
``not code''. Then, based on that information, we merged consecutive
paragraphs labeled as ``code'' and used a \js\ parser to check
well-formedness of the corresponding code fragment. Using that method
we were able to retrieve a total of \Fix{XX} files (\jsc{}=\Fix{XX},
\veight{}=\Fix{XX}, \smonkey{}=\Fix{XX}). All those files were
included in Table~\ref{tab:test-suites}.  Surprisingly, we did not
find a public classifier to solve the problem above. For space, we
summarize the solution that worked the best in the following. The
classifier that performed best for this case uses
a standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain
  what this ``Embeddings'' thing does at a high-level. Also, if this
  stuff exists why we did not find a solution off-the-shelf?} that
builds on a neural net~\Fix{cite} to keep a dictionary of words and the
similarity distance among them\Mar{but we are talking about
  sentences. how does it go from words to sentences? Note that many
  words from the ``code'' vocabulary are from English!}. In more
detail, the classification model uses a Convolutional Neural
Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
  meaning for each layer?} and has been trained and evaluated using a
dataset with 25K samples of English paragraphs and 25K snippets of
\js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
evaluate the model and obtained a predicted accuracy of
\Fix{98\%}. This classifier is publicly available from our website as
a separate component.

@@

Figure~\ref{fig:workflow} illustrates the 
differential testing infrastructure used in part of this study. It takes on
input a list of JS files and generates warnings on output. Boxes in
the figure denote encapsulation, arrowed lines denote data flow, and
the cycle icons denote repetition--the leftmost icon indicates that
each file in the input list will be analyzed in separate whereas the
rightmost icon shows that a single file will be fuzzed multiple times.
The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure ignores the input. Otherwise, it considers the input as
potentially fault-revealing; hence, interesting for human
inspection. The infrastructure uses the
open-source tool eshost-cli~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.\Mar{any difference in
  output is considered for reporting? are there any
  filtering?}

@@

It is worth noting that a number of reasons exist, other than a bug,
to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
and ~\ref{tab:false-positives}) and there is no clear automatic
approach to precisely distinguish false and true positives. As such, a
human needs to inspect the warning to classify the issue. As mentioned
earlier, this justifies why differential testing is challenging to
automate at the functional level. To facilitate inspection, we
prioritized warnings and clustered them in groups. We describe these
strategies in the following.

@@

We prioritized warnings based on their types, reflecting likelihood of
manifesting a real bug. We defined two types---``\hi{}'' and
``\lo{}''.

Warnings of the kind ``\hi{}'' are associated with the cases where the
test code executes without violating any internal checks, but it
violates an assertion declared in the test itself or its harness. The
rationale is that the test data is more likely to be valid in this
case as execution does not raise exceptions in application
code. Warnings of kind ``lo'' cover the remaining cases. These
warnings are more likely to be associated with invalid inputs. They
reflect the cases where the anomaly is observed during the execution
of application functions as opposed to assertions. We observed that
different engines often check pre-conditions of functions
differently. It can happen, for example, that one engine enforces a
weaker pre-condition, compared to another engine, on the inputs of a
function and that is acceptable.\Comment{ For instance, it is
  acceptable to pass values greater than \Fix{x} to function
  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
the infrastructure would report a warning that is more likely to be
associated with an invalid input produced by the fuzzer, \ie{}, it is
likely to be a ``bug'' in the test code as opposed to a bug in the
engine. Recall that, for differential testing, we only use seed tests
that pass in all engines.

Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
example, the test instantiates an \CodeIn{ArrayBuffer} object and
stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case from the
function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
engine did not throw any exception, as can be confirmed from the
report that our infrastructure produces starting with text ``Engine
Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
a case of undocumented precondition. It was fixed by
\chakra\ developers and is no longer present in the most recent
release of \chakra.

@@

%% Prioritization helps to steer our focus to the warnings more likely to
%% reveal bugs, but there could be several tests producing similar
%% warnings.

Clusterization is complementary to prioritization; it helps to group
similar warnings reported by our infrastructure. We only clustered
``\lo'' warnings as ``\hi'' warnings produce messages that arise from
the test case, which are typically distinct.

Figure~\ref{fig:lo-truepositive} shows, at the bottom, the identifier
of an engine, the exception it raises, and the message it produces on
a ``\lo'' warning.  This sequence of engine id, exception, and error
message triples defines a warning signature that we use for
clustering. It is worth mentioning that we filter references to code
in messages as to increase ability to aggregate warnings from
different test sources. Any warnings, including this one, that has
this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

@@

@@
